\documentclass[10pt]{article}
\usepackage{enumitem}
\usepackage[left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{ltablex}
\usepackage{setspace}
\usepackage{tabularx}

% Change itemize bullet type
\renewcommand{\labelitemi}{$\_$}

% Change line spacing
\renewcommand{\baselinestretch}{1.08}

% TimeFrame
% #1 Start Year
% #2 End Year
% #3 Length of time
\newcommand{\timeFrame}[3] {
  \if\relax\detokenize{#2}\relax
    #1
    % {\space\space\space\space\space#1}
  \else
    #1 - #2
  \fi
  \newline
  \scriptsize \textit{#3}
}

%% Work experience
% #1 Employer/Header
% #2 Title
% #3 Location
% #4 URL
% #5 Description
% #6 Technologies used
\newcommand{\entry}[6] {
  % #1 Employer/Header
  \textbf{#1}
  % #2 Title
  \if\relax\detokenize{#2}\relax
  \else
       - \textsc{#2}
  \fi
  % #3 Location
  \if\relax\detokenize{#3}\relax
  \else
      - \textsc{#3}
  \fi
  % #4 URL
  \if\relax\detokenize{#4}\relax
  \else
      - \href{https://#4}{#4}
  \fi
  % #4 Description
  \newline #5
  % #5 Technologies used
  \if\relax\detokenize{#6}\relax
  \else
      \newline \textsc{Technology:} #6
  \fi
  \\
}

% Draw a horizontal line in the second column
\newcommand{\horizontalLine}[0] {
    \noindent\rule{.90\linewidth}{0.4pt}
}

\begin{document}
\pagenumbering{gobble}

\begin{tabularx}{\linewidth}{>{\hsize=.10\hsize}X>{\hsize=.90\hsize}X}

%% Header
{\bfseries\large Adam McNeil} &
St. Louis, Missouri - \href{https://github.com/adamMcneil}{github.com/adamMcneil}\newline
{(636) 312-7281 \hspace{5.5mm} - \href{mailto:adamwmcneil@gmail.com}{adamwmcneil@gmail.com}} \\[5pt]

%% Profile
\textbf{Profile} &
{
  I graduated from the University of Illinois Urbana-Champaign with a Master's of Computer Science in 2025.
  My coursework focused on distributed systems and data storage.
  I have the most professional experience with Java, SQL, and Git working as a software developer intern at NISC.
  However, I have experience in a wide range of languages and technologies like: TypeScript, Rust, OCaml, Golang, C\#, Svelte, Tailwind, Neovim, Linux, Unity.
  % \newline
} \\

%% Experience
\textbf{Experience} & \horizontalLine \\

% NISC 
\timeFrame{2023}{2024}{Two Years} &
\entry{NISC}
  {Software Developer Intern}
  {Lake St. Louis, Missouri}
  {}
  {
  - Helped maintain batch processing workflow written in Java. \newline
  - Streamlined data retrieval process from an Oracle database. \newline
  - Created a test environment for migrating to a Postgres Database. \newline
  - Wrote scripts in PowerShell to automate code base analysis and modification.
  }
  {Java, PowerShell, Git, PostgreSQL, Oracle, Docker, Gradle, Windows \newline}

% Oasis Digital
\timeFrame{2022}{}{Nine months} &
\entry{Oasis Digital}
  {Software Development Intern}
  {Chesterfield, Missouri}
  {}
  {
  - Designed and developed a 3D project planning application using Unity. \newline
  - Used Firebase to manage and store persistent data. \newline
  - Competed in a company-wide game jam, successfully developing a game within a single day.
  }
  {C\#, Unity, Git, FireBase}


\textbf{Projects} & \horizontalLine \\
% Projects
\timeFrame{2021, 2025}{}{} &
\entry{Lichess Engine}
  {}
  {}
  {https://github.com/adamMcneil/chess-engine}
  {
    - Developed a Lichess bot in Java. \newline
    - Flame graphs and other performance metrics were used to identify the slow portion of code that needed to be optimized. \newline
    - Developed a unit and integration test suite. \newline
    - Implemented minimax algorithm with alpha-beta pruning to select the best move.
  }
  {Java, IntelliJ, Gradle, Git
    \newline
  }


\timeFrame{2023}{2024}{} &
\entry{Fullstack Project}
  {}
  {}
  {https://github.com/adamMcneil/mcneil-web-games}
  {
  - Developed web API in Rust programming language using Rocket Rust web framework. \newline
  - Developed static front end in Svelte and Tailwind. \newline
  - Deployed CI/CD pipeline with Render and GitHub pages to host backend and frontend, respectively.
  }
  {Rust, Svelte, TypeScript, HTTP, CSS, Tailwind, Render, Git
    \newline
  }

\timeFrame{2024}{}{} &
\entry{Streaming Platform}
  {}
  {}
  {Distributed Systems Course Project}
  {
  - Developed a distributed group membership service. \newline
  - Developed a distributed file system using the group membership service. \newline
  - Developed a distributed stream-processing framework similar to Spark Streaming. \newline
  - Implemented with gRPC. \newline
  - Used Docker to create a virtual testing environment.
  }
  {Go, Protocol Buffers, gRPC, Docker, Spark Streaming
    \newline
  }


\timeFrame{2024}{}{} &
\entry{UDP Controller}
  {}
  {}
  {}
  {
    - Implemented a simple game in Bevy to act as a server. \newline
    - Created a mobile app that communicates over the local area network with a central server using WebSockets.
  }
  {Rust, Bevy, Android Studio, Kotlin}

%% Education
\textbf{Education} & \horizontalLine \\

% Master's (4.00 GPA)
\timeFrame{Aug 2024}{May 2025}{One Year} &
\entry{University of Illinois Urbana-Champaign}
  {}
  {Urbana-Champaign, Illinois}
  {GPA: 3.80}
  {
  Master of Computer Science \newline
  }
  {}

% Bachelor's  (3.948 GPA)
\timeFrame{Aug 2021}{May 2024}{Three Years} &
\entry{University of Science and Technology}
  {}
  {Rolla, Missouri}
  {GPA: 3.94}
  {
  Bachelor of Science in Computer Science, Minor in Mathematics
  }
  {}

\end{tabularx}

\end{document}
